---
title: "MODULES 07 and 08"
author: "Caitlin Leslie"
date: "February 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Challenge 01

1. First, create a vector of 1 word character strings comprising the first line of the Gettysburg address: “Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal.”


```{r}
library(stringr)
getty<-c("Four score and seven years ago our fathers brought forth on this continent a new nation conceived in Liberty and dedicated to the proposition that all men are created equal")
gettym<-str_split(getty, " ", simplify=TRUE)
gettym
```

2. Then, extract every third element of this vector.

```{r}
gettym3<-gettym[seq(from=1, to=30, by=3)]
gettym3
```

## Challenge 02

```{r}
m<-matrix(data=1:80, nrow=8, ncol=10, byrow=FALSE)
m
```

1. Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x

```{r}
x<-m[,c(2,3,6)]
x

```

2. Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x

```{r}
x<-m[6:8,]
x
```

3. Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x

```{r}
x<-m[2:6, 2:9]
x
```

## Challenge 03

1.  Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)

```{r}
a<-array(data=400:1, dim=c(5,5,4,4))
a
```

2. Given this matrix, what would the following return?
* a[1, 1, 1, 2]

```{r}
a[1,1,1,2]
```
    
* a[2, 3, 2, ]

```{r}
a[2,3,2, ]
```
    
* a[1:5, 1:5, 3, 3]

```{r}
a[1:5, 1:5, 3, 3]
```

## Challenge 04

1. Create a list representing the (simplified) primate taxonomy

```{r}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Tarsioidea <- c("Tarsiidae")
Anthropoidae <- matrix(data=(rbind(Platyrrhini, Catarrhini)), nrow=2, ncol=3, byrow=FALSE)
rownames(Anthropoidae) <- c("Platyrrhini", "Catarrhini")
Haplorhini <- list(Anthropoidae, Tarsioidea)
names(Haplorhini) <- c("Anthropoidea", "Tarsioidea")

Lorisoidea <- c("Lorisidae", "Galagidae")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae") 
Strepsirhini <- list(Lorisoidea, Lemuroidea)
names(Strepsirhini) <- c("Lorisoidea", "Lemuroidea")

Primates<- list(Haplorhini, Strepsirhini)
names(Primates) <- c("Haplorhini", "Strepsirhini")
Primates
```

## Notes

Uploading random_people.csv file as a data frame

```{r}
df<-read.csv(file="C:\\Users\\caibe\\Desktop\\random_people.csv.txt", sep=",", header=TRUE, stringsAsFactors=FALSE)
```

If that doesn't work:

```{r}
f<-file.choose() #this opens a dialog box where I can manually choose the file to import
```

##Challenge 05

1. Store the following numbers as a 5 x 3 matrix: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROWWISE.


```{r}
m<-matrix(data=c(3,0,1,23,1,2,33,1,1,42,0,1,41,0,2), nrow=5, ncol=3, byrow=TRUE)
m
```

2. Then, do the following:

* Coerce the matrix to a data frame.

```{r}
df<- data.frame(m)
df
```

* As a data frame, coerce the second column to be logical-valued (Boolean)

```{r}
df[,2]<-as.logical(df[,2])

```

* As a data frame, coerce the third column to be factor-valued

```{r}
df[,3]<-as.factor(df[,3])
```

3. When you are done, use the str() command to show the data type for each variable in your dataframe.

```{r}
str(df)

```
